First Class Pattern Matching in a Deeply Embedded Domain Specific Language\\ \large{Not For Distribution}

### 2020-07-11 paper/paper.tex
Fixed typo
Format paper for GPCE; add Mark to author list

%% This is file `sample-acmsmall.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `acmsmall')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-acmsmall.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigplan,screen]{acmart}
\usepackage[switch]{lineno}
\usepackage{booktabs}
\usepackage{listings}
\usepackage{tcolorbox}
\usepackage{tikz}
\usepackage{tkz-graph}
\usepackage{stmaryrd}
\usepackage{amsmath}

@@

% \renewcommand{\linenumberfont}{\color{blue}}
\renewcommand\linenumberfont{\normalfont\tiny\sffamily\color{red}}

@@

\acmConference[Haskell '20]{Haskell '20: Proceedings of the 13th
  ACM SIGPLAN International Symposium on Haskell}{August 27 -- 28, 2020}{New Jersey, United States,}
\acmBooktitle{Haskell '20: ACM SIGPLAN International Symposium on Haskell,
  August 27 -- 28, 2020, New Jersey, United States}
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

@@

@@

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
% \renewcommand{\shortauthors}{Trovato and Tobin, et al.}
\renewcommand{\shortauthors}{Young and Gill}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Domain specific languages (DSLs) provide a powerful tool for abstracting over
  a class of problems. In this paper, we introduce a technique for representing
  algebraic data types and pattern matching in a DSL embedded in Haskell. This
  representation is mechanized through the use of GHC Generics and and GHC Core plugin.
\end{abstract}

@@

\linenumbers
\section{Introduction}

>>>>

%% This is file `sample-acmsmall.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `acmsmall')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-acmsmall.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigplan,anonymous,review]{acmart}
\usepackage[switch]{lineno}
\usepackage{booktabs}
\usepackage{listings}
\usepackage{tcolorbox}
\usepackage{tikz}
\usepackage{tkz-graph}
\usepackage{stmaryrd}
\usepackage{amsmath}

@@

% \renewcommand{\linenumberfont}{\color{blue}}

% \renewcommand\linenumberfont{\normalfont\tiny\sffamily\color{red}}

@@

\acmConference[GPCE '20]{Haskell '20: Proceedings of the 13th
  ACM SIGPLAN International Symposium on Haskell}{November 15 -- 20, 2020}{Chicago, Illinois, United States}
\acmBooktitle{Proceedings of the 19th ACM SIGPLAN International
Conference on Generative Programming: Concepts and Experiences (GPCE '20)
  November 15 -- 20, 2020, Chicago, Illinois, United States}
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

@@

\author{Mark Grebe}
\email{grebe@ucmo.edu}

@@

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
% \renewcommand{\shortauthors}{Trovato and Tobin, et al.}
\renewcommand{\shortauthors}{Young, Grebe and Gill}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Domain specific languages (DSLs) provide a powerful tool for abstracting over
  a class of problems. In this paper, we introduce a technique for representing
  algebraic data types and pattern matching in a DSL embedded in Haskell. This
  representation is mechanized through the use of GHC Generics and a GHC Core plugin.
\end{abstract}

@@

\section{Introduction}
